Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-25 paper/paper-DrexelFormat.tex
updated paper - back-propagation

The output from hidden layer can be computed
$$\vec{h} = \bold{h}(\vec{x}\bold{u}+\vec{c}) = \bold{h}(\vec{X}\bold{U})$$
The output of the neural network can be computed
$$\vec{o} = \bm{\phi}(\vec{h}\bold{w}+\vec{b}) = \bm{\phi}(\vec{H}\bold{W})$$
Therefore, final equation for two layer neural network is
$$\vec{o} = \bm{\phi}(\bold{h}(\vec{x}\bold{u}+\vec{c})\bold{w}+\vec{b})$$

@@

\subsubsection{Backpropagation}\label{subsubsec:BP}
{\color{blue} add backpropagation}

%Training neural network means finding weights and biases. Process of finding weights and biases is 'training neural network'. This part shows how to train neural network by backpropagation.
%Let $\vec{x} \in \mathbb{R}^n$ be input, $\vec{y} \in \mathbb{R}^m$ be label, $\vec{b} \in \mathbb{R}^m$ be bias, and  $\bold{w}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be transform matrix.

>>>>

To compute output of MNN, forward-propagation is used. forward-propagation is to pass input $\vec{x}$ to output through hidden layers \cite{murphy2012machine}. For example, the output from hidden layer on Figure \ref{fig:MNN} can be computed
$$\vec{h} = \bold{f}(\vec{x}\bold{v}+\vec{c}) = \bold{f}(\vec{X}\bold{V})$$
Then output layer uses output from hidden layer as input. The output of the neural network can be computed
$$\vec{o} = \bold{g}(\vec{h}\bold{w}+\vec{b}) = \bold{g}(\vec{H}\bold{W})$$
Therefore, final equation for two layer neural network is
$$\vec{o} = \bold{g}(\bold{h}(\vec{x}\bold{v}+\vec{c})\bold{w}+\vec{b})$$

@@

\subsubsection{Back-propagation}\label{subsubsec:BP}
Training neural network means finding weights and biases. Similar as forward-propagation, back-propagation is used when MNN is trained. As forward-propagation passes input $\vec{x}$ to output, back-propagation passes error from output layer to hidden layer \cite{murphy2012machine}. Error function or loss function usually uses sum square error as follow:
$$E=L(\vec{y}, \vec{o}) = \frac{1}{2}\sum_{i}(y_i-o_i)^2$$
Where $\vec{y}$ is expected output from MNN. It means that the goal of MNN is to find weights and biases that make $\vec{o}$ have same values of $\vec{y}$. Therefore, error function is the function on weights and biases. For example, error function of two layers MNN can be written as follow:
$$E=J(\bold{V}, \bold{W})$$

To update weights, let $\vec{h'}=\vec{X}\bold{V}$ be input for hidden layer activation function $\bold{f}$ and $\vec{o'}=\vec{H}\bold{W}$ be input for output layer activation function $\bold{g}$. So $\vec{h}=\bold{f}(\vec{h'})=\bold{f}(\vec{X}\bold{V})$ and $\vec{o}=\bold{g}(\vec{o'})=\bold{g}(\vec{H}\bold{W})$. Let $V_{ij}$ be $i$th neuron weight in hidden layer for input $X_j$ and $W_{ij}$ be $i$th neuron weight in output layer for input $H_j$.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.7\textwidth]{pictures/figures/BP1.png}
    \caption{Back-propagation for $W_{ij}$}
    \label{fig:BP1}
\end{figure}

Let's first update $W_{ij}$ and Figure \ref{fig:BP1} shows detail of output layer related with ${W_{ij}}$. The updated weight ${{W_{ij}}^{next}}$ can be calculated as follow:
$${{W_{ij}}^{next}}=W_{ij} - \eta\frac{\partial E}{\partial W_{ij}}$$ where $\eta$ is learning rate. The equation tells to remove error, updated weight should be move opposite direction of gradient of error function. The method is called 'gradient descent'.

Let's compute $\frac{\partial E}{\partial W_{ij}}$
$$
\frac{\partial E}{\partial W_{ij}}
= \frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial W_{ij}}
= \frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
$$
So the equation has three parts.

First part is
$$
\frac{\partial o'_i}{\partial W_{ij}}
= \frac{\partial}{\partial W_{ij}}\sum_k(H_kW_{ik})
= \frac{\partial}{\partial W_{ij}}(H_jW_{ij})
= H_j
$$

Assume all activation function is sigmoid function $sigm()$ then second part is
$$
\frac{\partial o_i}{\partial o'_i}
= \frac{\partial}{\partial o'_i}sigm(o'_i)
= sigm(o'_i)\{1-sigm(o'_i)\}
= o_i(1-o_i)
$$

Assume error function is sum square then the last part is
$$
\frac{\partial E}{\partial o_i}
= \frac{\partial}{\partial o_i}\frac{1}{2}\sum_k(y_k-o_k)^2
= \frac{\partial}{\partial o_i}\frac{1}{2}(y_i-o_i)^2
= (o_i-y_i)
$$

Therefore,
$$
{{W_{ij}}^{next}}
= W_{ij} - \eta\frac{\partial E}{\partial W_{ij}}
= W_{ij} - \eta\frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial o'_i}\frac{\partial o'_i}{\partial W_{ij}}
= W_{ij} - \eta(o_i-y_i)o_i(1-o_i)H_j
$$

Before moving to update weights for hidden layer, define $\delta_i$ as follow:
$$
\delta_i
= \frac{\partial E}{\partial o'_i}
= \frac{\partial E}{\partial o_i}\frac{\partial o_i}{\partial o'_i}
$$

The $\delta_i$ is useful because it is shared when back-propagation updates all weights related with $i$th neuron. Also the $\delta_i$ is used when back-propagation updates weights on hidden layers.

\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{pictures/figures/BP2.png}
    \caption{Back-propagation for $V_{ij}$}
    \label{fig:BP2}
\end{figure}

The next step is to update weights in hidden layer. Let's update $V_{ij}$ and Figure \ref{fig:BP2} shows detail of neural network related with $V_{ij}$. The updated weight ${{V_{ij}}^{next}}$ can be calculated as follow:
$${{V_{ij}}^{next}}=V_{ij} - \eta\frac{\partial E}{\partial V_{ij}}$$ where $\eta$ is learning rate. The equation is similar as ${{W_{ij}}^{next}}$

Let's compute $\frac{\partial E}{\partial V_{ij}}$
$$
\frac{\partial E}{\partial V_{ij}}
= \frac{\partial E}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
= \frac{\partial E}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
$$
So the equation also has three parts.

First part is
$$
\frac{\partial h'_i}{\partial V_{ij}}
= \frac{\partial}{\partial V_{ij}}\sum_k(X_kV_{ik})
= \frac{\partial}{\partial V_{ij}}(X_jV_{ij})
= X_j
$$

Assume the activation function for hidden layer is also sigmoid function $sigm()$ then second part is
$$
\frac{\partial h_i}{\partial h'_i}
= \frac{\partial}{\partial h'_i}sigm(h_i)
= sigm(h'_i)\{1-sigm(h'_i)\}
= h_i(1-h_i)
$$

Then the last part is
$$
\frac{\partial E}{\partial h_i}
= \sum_k(\frac{\partial E}{\partial o'_k}\frac{\partial o'_k}{\partial h_i})
= \sum_k(\delta_kw_{ki})
$$

Therefore,
$$
{{V_{ij}}^{next}}
= V_{ij} - \eta\frac{\partial E}{\partial V_{ij}}
= W_{ij} - \eta\frac{\partial E}{\partial h_i}\frac{\partial h_i}{\partial h'_i}\frac{\partial h'_i}{\partial V_{ij}}
= W_{ij} - \eta\sum_k(\delta_kw_{ki})h_i(1-h_i)X_j
$$

Notice that as forward-propagation sends output of a layer as input of next layer, back-propagation sends error of a layer to previous layer. For example, the $\delta_i=\frac{\partial E}{\partial o'_i}$ is error on output layer then sends it to hidden layer.
